Full Brain Blood-Oxygen-Level-Dependent Signal Parameter Estimation Using Particle Filters

### 2010-08-25 doc/paper/main.tex
mostly done, a few better images from the defense

\begin{figure}[!t]
\subfloat[Region labels for simulated slice.]
{\includegraphics[width=3cm]{images/simregions.png}\label{fig:simslice_mask}}
\hfil
\subfloat[Mutual Information Map. Scale is bits. Higher (yellow) is better.]
{\label{fig:sim_hm_mi} \includegraphics[width=4cm]{images/sim_hm_15_6.png}}
\subfigure{\includegraphics[width=.6cm]{images/scale6.png}}
\caption{Comparison of activation with greymatter, parameter regions.}
\label{fig:simslice_hm}
\end{figure}

@@

\subsection{Real Data}
\begin{figure*}
\centering
\subfigure{\label{fig:hm_spm} \includegraphics[scale=3]{spm_hm}}
\subfigure{\label{fig:scale_spm} \includegraphics[scale=.35]{scale1}}
\caption{SPM results. Units of activation are in Student's $t$-scores; higher indicates higher
        assurance that the signal cannot have occurred through noise alone.}
\label{fig:hm_canon_spm}
\end{figure*}

\begin{figure*}
\centering
\subfigure{\label{fig:hm_mi} \includegraphics[scale=3]{hm_mi_strict}}
\subfigure{\label{fig:scale_mi} \includegraphics[scale=.35]{scale4}}
\caption{Particle filter results. Units of activation are in mutual information; higher
    indicates more assured activation.}
\label{fig:hm_canon_spm}
\end{figure*}

>>>>

\begin{figure}[!t]
\subfloat[Region labels for simulated slice.]
{\includegraphics[height=4.5cm]{simregions.png}\label{fig:simslice_mask}}
\hfil
\subfloat[Mutual Information Map. Scale is bits. Higher (yellow) is better.]
{\label{fig:sim_hm_mi} \includegraphics[height=4.5cm]{sim_hm_15_6.png}}
\caption{Comparison of activation with greymatter, parameter regions.}
\label{fig:simslice_hm}
\end{figure}

@@

\subsection{Real Data}
\begin{figure*}
\centering
\subfloat{\label{fig:hm_spm} \includegraphics[scale=3]{spm_hm}}
\subfloat{\label{fig:scale_spm} \includegraphics[scale=.35]{scale1}}
\caption{SPM results. Units of activation are in Student's $t$-scores; higher indicates higher
        assurance that the signal cannot have occurred through noise alone.}
\label{fig:hm_canon_spm}
\end{figure*}

\begin{figure*}
\centering
\subfloat{\label{fig:hm_mi} \includegraphics[scale=3]{hm_mi_strict}}
\subfloat{\label{fig:scale_mi} \includegraphics[scale=.35]{scale4}}
\caption{Particle filter results. Units of activation are in mutual information; higher
    indicates more assured activation.}
\label{fig:hm_mi_res}
\end{figure*}
